Pages written in a given year

### 2023-01-12 src/pages.Rmd
Created master page for 1999

```{r}
for (four_digit_year in c("2014")) {
  two_digit_year <- str_sub(four_digit_year, 3, 4)
  yaml_text <- write_yaml(two_digit_year)
  l <- write_list(two_digit_year)
  n <- dim(l)[1]
  fn <- glue("../text/{two_digit_year}/{four_digit_year}.md")
  write_lines(
    yaml_text, 
    file=fn,
    append=FALSE)
  write_lines(
    glue("New website ({n} files)\n\n"),
    file=fn,
    append=TRUE)
  write_lines(
    l$links, 
    file=fn,
    append=TRUE)
  problem_files <- c(
    paste(l$f, l$date_list)[l$bad_date],
    paste(l$f, l$source_list)[l$bad_source])
  all_good <- "All files passed date and source quality checks"
  if (length(problem_files)==0) problem_files <- all_good
  write_lines(
    c("\n", problem_files),
    file=fn,
    append=TRUE)
}
```

@@

`r paste(problem_files, collapse="\n")`

>>>>

```{r}
for (four_digit_year in c("1999")) {
  two_digit_year <- str_sub(four_digit_year, 3, 4)
  yaml_text <- write_yaml(two_digit_year)
  l <- write_list(two_digit_year)
  n <- dim(l)[1]
  fn <- glue("../text/{two_digit_year}/{four_digit_year}.md")
  write_lines(
    yaml_text, 
    file=fn,
    append=FALSE)
  write_lines(
    glue("New website ({n} files)\n\n"),
    file=fn,
    append=TRUE)
  write_lines(
    l$links, 
    file=fn,
    append=TRUE)
  problem_files <- c(
    paste(l$f, l$date_list)[l$bad_date],
    paste(l$f, l$source_list)[l$bad_source])
  all_good <- "All files passed date and source quality checks"
  if (length(problem_files)==0) problem_files <- all_good
  write_lines(
    "\n\n### Quality check\n",
    file=fn,
    append=TRUE)
  write_lines(
    paste0("+ ", problem_files),
    file=fn,
    append=TRUE)
}
```

@@

`r paste(paste("1.", problem_files), collapse="\n")`
